A thesis draft

### 2018-11-21 res/sections/08-Background.tex

\begin{figure}
  \centering
  \includegraphics[scale=0.2]{networkslicing}
  \caption{The three layers model of network
  slicing~\cite{alliance2016description}}
  \label{chap:background:img:network_slicing}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=2]{etsi_arch}
  \caption{Network Function Virtualization reference
  architecture~\cite{etsi2013gs}}
  \label{chap:background:img:etsi_arch}
\end{figure}

@@

The \emph{Network Service Header} (NSH), used by SFC environment for
encapsulation is described in~\cite{rfc8300} and it consider three main fields
as represented in Figure~\ref{chap:background:img:nshformat}: Base Header,
Service Path Header and Context Header.
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshformat}
  \caption{Network Service Header~\cite{rfc8300}}
  \label{chap:background:img:nshformat}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshbase}
  \caption{Network Service Header~\cite{rfc8300}}
  \label{chap:background:img:nshformat}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshservicepath}
  \caption{NSH Service Path Header~\cite{rfc8300}}
  \label{chap:background:img:nshpath}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshtype1}
  \caption{NSH MD Type \texttt{0x1}~\cite{rfc8300}}
  \label{chap:background:img:nshtype1}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshtype2}
  \caption{NSH MD Type \texttt{0x2}~\cite{rfc8300}}
  \label{chap:background:img:nshtype2}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshtype2variable}
  \caption{Variable-Length Context Header~\cite{rfc8300}}
  \label{chap:background:img:nshtype2variable}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.55]{5garchitecture}
  \caption{5G Architecture~\cite{alliance20155g}}
  \label{chap:background:img:5garchitecture}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.2]{networkslicing}
  \caption[The three layers model of network slicing]{The three layers model of
    network slicing~\cite{alliance2016description}}
  \label{chap:background:img:network_slicing}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=2]{etsi_arch}
  \caption[Network Function Virtualization reference architecture]{Network
    Function Virtualization reference architecture~\cite{etsi2013gs}}
  \label{chap:background:img:etsi_arch}
\end{figure}

@@

The \emph{Network Service Header} (NSH), used by SFC environment for
encapsulation is described in~\cite{rfc8300} and it consider three main fields
as represented in Figure~\ref{chap:background:img:nshformat}: Base Header,
Service Path Header and Context Header.
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshformat}
  \caption[Network Service Header]{Network Service Header~\cite{rfc8300}}
  \label{chap:background:img:nshformat}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshbase}
  \caption[Network Service Header]{Network Service Header~\cite{rfc8300}}
  \label{chap:background:img:nshformat}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshservicepath}
  \caption[NSH Service Path Header]{NSH Service Path Header~\cite{rfc8300}}
  \label{chap:background:img:nshpath}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshtype1}
  \caption[NSH MD Type \texttt{0x1}]{NSH MD Type \texttt{0x1}~\cite{rfc8300}}
  \label{chap:background:img:nshtype1}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshtype2}
  \caption[NSH MD Type \texttt{0x2}]{NSH MD Type \texttt{0x2}~\cite{rfc8300}}
  \label{chap:background:img:nshtype2}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{nshtype2variable}
  \caption[Variable-Length Context Header]{Variable-Length Context
    Header~\cite{rfc8300}}
  \label{chap:background:img:nshtype2variable}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.55]{5garchitecture}
  \caption[5G Architecture]{5G Architecture~\cite{alliance20155g}}
  \label{chap:background:img:5garchitecture}
\end{figure}
